Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
intro to FP

The vector of parametric uncertainties  $\Delta{p}$ for $G(z)$ is defined by:
\begin{equation}
\Delta{p}=\begin{bmatrix}
\hat{b_{0}} - b_{0}\\
\hat{b_{1}} - b_{1}\\
\vdots \\
\hat{b}_{M_G} - b_{M_{G}}\\
\hat{a_{0}} - a_{0}\\
\hat{a_{1}} - a_{1}\\
\vdots\\
\hat{a}_{N_G} - a_{N_{G}}\\
\end{bmatrix}=\begin{bmatrix}
\vec{\hat{b}}\\
\vec{\hat{a}}
\end{bmatrix}-\begin{bmatrix}
\vec{b}\\
\vec{a}
\end{bmatrix}
\end{equation}

\red{[where is this new variable used later?]}

A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ 
\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
The {\sc synthesise} phase uses a BMC-based verifier to 
compute a solution ($N_c$,$D_C$). An important remark is that this 
controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
domain.  
\cdsay{integrate the following with Dario}
Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
using Fixed-Point bit vectors with integer size $I_b$ and fractional
size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

>>>>

The vector of parametric coefficient uncertainties $\Delta{p}$ of $\Delta{G}_p(z)$ is defined by:
\begin{equation}
\Delta{p}=\begin{bmatrix}
\hat{b_{0}} - b_{0}\\
\hat{b_{1}} - b_{1}\\
\vdots \\
\hat{b}_{M_G} - b_{M_{G}}\\
\hat{a_{0}} - a_{0}\\
\hat{a_{1}} - a_{1}\\
\vdots\\
\hat{a}_{N_G} - a_{N_{G}}\\
\end{bmatrix}=\begin{bmatrix}
\vec{\hat{b}}\\
\vec{\hat{a}}
\end{bmatrix}-\begin{bmatrix}
\vec{b}\\
\vec{a}
\end{bmatrix}
\end{equation}

A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ 
\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
The {\sc synthesise} phase uses a BMC-based verifier to 
compute a solution ($N_c$,$D_C$). An important remark is that this 
controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
domain.
A second remark is that the synthesis and verification engines use fixed/floating point arithmetic,
therefore we also need to examine the effect of discretization during these operations.
\cdsay{integrate the following with Dario}
Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
using Fixed-Point bit vectors with integer size $I_b$ and fractional
size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}
